A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-21 analysis/paper.Rmd
add Overview section to paper.Rmd and edit bib file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
x <- 1 + 1
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Methods

## Overview
The original model was implemented in R (v3.5.2) [team2013r] with web application (https://johnquattrochi.com/bias/) to show that indirect method such as surveying can underestimate U5M by 0-41% in populations where 0-40% of the people are affected by HIV/AIDS. The model was written using the R language [team2013r] and some of the main packages used were tidyverse (v1.2.1) and foreach (v1.4.4). The original implementation utilized the doReids package (v1.1.1) that offers a back-end server for parallel processing that was not adopted in our replication due to the limitation in resources. In order to complete the simulation for constructing the model in a reasonable time frame without parallel computing, we reduced the number of populations used in the simulation input from 4480 to 1000. The code provided the author on Github (https://github.com/jquattro/hiv-childmort-bias) was mostly well-organized and documented. However, we discovered some mistakes regarding output inconsistency and wrong variable names. Despite the debugging process, we were able to replicate the implementation.

## Model Description
